---
title: 'MAGOLEGO SNA 2019 Egor Krotov HW #4'
author: "Egor Krotov"
date: '21 мая 2019 г '
output: html_document
---

# Network Epidemics

```{r}
library(igraph)
library(EpiModel)
library(xtable)
```

## SIR Model

You need to perform epidemic SIR model on different types of networks: Try different parameters for network generation: 

```{r, echo = F, message = F, warning = F}
generated = list()
generated$renyi = erdos.renyi.game(n = 300, p.or.m = 0.03, type=c("gnp"))
generated$watts = watts.strogatz.game(dim = 1, size = 1000, nei = 3, p = 0.01)
generated$barabasi = barabasi.game(n = 300,m = 30 , directed=FALSE)

table_net = read.table("Net.txt")
table_net = t(as.matrix(table_net))

generated$network = graph(table_net)
no.clusters(generated$renyi)
no.clusters(generated$barabasi)
no.clusters(generated$watts)
no.clusters(generated$network)

#Все виды сетей я создал в одном списке. Для них я использовал разные параметры для типов сетей. Чаще всего получается по 1 кластеру на каждую сеть. В Barabasi иногда получается больше, до 10. При коспиляции возникает ошибка Error in (function (edges, n = max(edges), directed = TRUE) : At structure_generators.c:86 : Invalid (negative) vertex id, Invalid vertex id. Опытным путём я выяснил, что без первых 10 строк исходного файла она пропадает и не использовал эти данные.
``` 

Moreover perform modeling on real peer-to-peer network here
Your goal is to perform a research on epidemics: Use different values of parameters listed below

```{r}
beta = 2
gamma = 4
ntrials = 100
sim = lapply(generated, sir, beta=beta, gamma=gamma, no.sim=ntrials)

beta_s2 = 4
gamma_s2 = 8
trials_s2 = 300
sim_2 = lapply(generated, sir, beta=beta_s2, gamma=gamma_s2, no.sim=trials_s2)

beta_s3 = 6
gamma_s3 = 6
trials_s3 = 600
sim_3 = lapply(generated, sir, beta=beta_s3, gamma=gamma_s3, no.sim=trials_s3)

beta_s4 = 8
gamma_s4 = 2
trials_s4 = 1200
sim_4 = lapply(generated, sir, beta=beta_s4, gamma=gamma_s4, no.sim=trials_s4)

# Для каждого набора я составил свой набор параметров.
```

at least 3 different versions, for example:
• betta (4 6 8)
• gamma (8 6 2)
• niter (100 500 1000)
For some reason beta and gamma parameters should not be set below 0 and 1. Looks like they are somehow
normilized during simulation.
The code below can help you with plotting

```{r}
plot(sim$renyi)
plot(sim$barabasi, color="palegoldenrod", median_color="gold", quantile_color="gold")
plot(sim$watts, color="pink", median_color="red", quantile_color="red")
x.max = max(sapply(sapply(sim, time_bins), max))
y.max = 1.05 * max(sapply(sapply(sim, function(x) median(x)[["NI"]]), max, na.rm=TRUE))
plot(time_bins(sim$renyi), median(sim$renyi)[["NI"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, 100), xlab="Time", ylab=expression(N[I](t)))
lines(time_bins(sim$barabasi), median(sim$barabasi)[["NI"]], lwd=2, col="gold")
lines(time_bins(sim$watts), median(sim$watts)[["NI"]],lwd=2, col="red")
legend("topright", c("ER", "BA", "WS"),col=c("blue", "gold", "red"), lty=1)

#Number of infected, number of susceptible, number of recovered - all depends on time. The main ideas of these models are:  - Erdos-Renyi (ER) model: every possible edge is created with the same constant probability.  - Barabasi-Albert (BA) model: each new node is connected to existing nodes with a probability proportional to the number of links of these nodes.  - Watts-Strogatz (WS) model: accounts for clustering while retaining the short average path lengths of the ER model. At the plots we see that as time increases, we get that r(t) (fraction of the population that will get sick) stabilizes and so dr/dt = 0 and lines come to 0 - common thing for all the simulations. At the given simulation (2 4 100) for er model we see the peak, but rather small. For ba model we see the bigger peak relatively to other plots for ws model we don't see peaks - this connected with the fact that only 1 cluster for this model exists (see the result of function no.clusters(gl$ws)).
```

You need to plot three values on the graphics: Number of infected, number of suseprible, number of recovered - all depends on time.
As a result of this task, you need to provide 12 plots (one for each network with 3 diferent parameters) with explanation.

```{r}
plot(sim_2$barabasi, color="palegoldenrod", median_color="gold", quantile_color="gold")
plot(sim_2$watts, color="pink", median_color="red", quantile_color="red")
plot(sim_2$renyi)

x.max = max(sapply(sapply(sim_2, time_bins), max))
y.max = 1.05 * max(sapply(sapply(sim_2, function(x) median(x)[["NI"]]), max, na.rm=TRUE))

plot(time_bins(sim_2$renyi), median(sim_2$renyi)[["NI"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, 100), xlab="Time", ylab=expression(N[I](t)))
lines(time_bins(sim_2$barabasi), median(sim_2$barabasi)[["NI"]], lwd=2, col="gold")
lines(time_bins(sim_2$watts), median(sim_2$watts)[["NI"]],lwd=2, col="red")
legend("topright", c("ER", "BA", "WS"),col=c("blue", "gold", "red"), lty=1)

# At the given simulation (4 8 100) we see the same behaviour as at the previous simulation because of the proportion between them, but for the WS model the small peak appears and as time increases.
```


```{r}
# par(mfrow=c(3,1)) # combining plots
plot(sim_3$barabasi, color="palegoldenrod", median_color="gold", quantile_color="gold")
plot(sim_3$watts, color="pink", median_color="red", quantile_color="red")
plot(sim_3$renyi)

x.max = max(sapply(sapply(sim_3, time_bins), max))
y.max = 1.05 * max(sapply(sapply(sim_3, function(x) median(x)[["NI"]]), max, na.rm=TRUE))

plot(time_bins(sim_3$renyi), median(sim_3$renyi)[["NI"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, 200), xlab="Time", ylab=expression(N[I](t)))
lines(time_bins(sim_3$barabasi), median(sim_3$barabasi)[["NI"]], lwd=2, col="gold")
lines(time_bins(sim_3$watts), median(sim_3$watts)[["NI"]],lwd=2, col="red")
legend("topright", c("ER", "BA", "WS"),col=c("blue", "gold", "red"), lty=1)

#At the given simulation (6 6 500) we see absolutely different behaviour - there are relatively big peaks for ER and BA simulation, and as the time increases WS model is not coming to 0 for a long time and for BA and ER come to 0 very fast - this connected with the small number of trials.
```


```{r}
# par(mfrow=c(3,1)) # combining plots
plot(sim_4$renyi)
plot(sim_4$barabasi, color="palegoldenrod", median_color="gold", quantile_color="gold")
plot(sim_4$watts, color="pink", median_color="red", quantile_color="red")

x.max = max(sapply(sapply(sim_4, time_bins), max))
y.max = 1.05 * max(sapply(sapply(sim_4, function(x) median(x)[["NI"]]), max, na.rm=TRUE))

plot(time_bins(sim_4$renyi), median(sim_4$renyi)[["NI"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, 500), xlab="Time", ylab=expression(N[I](t)))
lines(time_bins(sim_4$barabasi), median(sim_4$barabasi)[["NI"]], lwd=2, col="gold")
lines(time_bins(sim_4$watts), median(sim_4$watts)[["NI"]],lwd=2, col="red")
legend("topright", c("ER", "BA", "WS"),col=c("blue", "gold", "red"), lty=1)

#At the given simulation (8 2 1000) because of a big value of beta parameter and small value of gamma we see the highest peaks of all the simulations and the typical coming to 0 for all the models. It connected with the formulas (ds/dt = - beta * s * x and dx/dt = beta * s * x - gamma * x) - the big increment at the time.
```

