---
title: 'MAGOLEGO SNA 2019 Semyon Gudkov HW #3'
author: "Semyon Gudkov"
date: '24 мая 2019 г '
output: html_document
---


## Yahoo Music Network

For this assignment, you have to load the part of Yahoo Music Network. Archive contains network in GML format and corresponding list of artists.

```{r}
library('igraph')

#Загружаю нужную библиотеку

yahoo_MUSIC = read.graph("music2K.gml", format = "gml")

yahoo_MUSIC.isolated.vertices = V(yahoo_MUSIC)[degree(yahoo_MUSIC) == 0]

#Для корректной работы надо избавиться от изолированных вершин
```

Edges in this network appear if enough number of users have given ratings to both music bands. Note, that edges are weighted with similarity of the ratings.

### 1. Preprocessing
This network needs to be preprocessed. Do the steps, described on seminar, to make it look properly. How many vertices and edges were deleted?

```{r}
ec_f1 = ecount(yahoo_MUSIC)
vc_f1 = vcount(yahoo_MUSIC)

yahoo_MUSIC = delete.vertices(yahoo_MUSIC, degree(yahoo_MUSIC) == 0)
proverka = is.simple(simplify(yahoo_MUSIC, remove.multiple=FALSE))

print(sprintf("IS SIMPLE: %s",proverka))

ec_f2 = ecount(yahoo_MUSIC)
vc_f2 = vcount(yahoo_MUSIC)

vc_raznica = vc_f1 - vc_f2
ec_raznica = ec_f1 - ec_f2

print(sprintf("Got deleted vertices and edges:  %d and %d ", vc_raznica, ec_raznica))
```

### 2. Clustering

Define clusters for this networks using one of the algorithms described on lectures and seminars:

```{r}
#Алгоритм fastgreedy работает без ошибок, поэтому я выбрал его

setka = fastgreedy.community(yahoo_MUSIC)
```

Compute density of obtained clusters:

```{r}
setka_dens  = 1:length(setka)
coming_c =  1:length(setka)
for (j in 1:length(setka)) 
{
tmp_graph = induced.subgraph(yahoo_MUSIC, which(setka$membership == j))
tmp_con = coming_c[j]
tmp_den = setka_dens[j]
tmp_con = ecount(tmp_graph)
tmp_den = graph.density(tmp_graph)
print(sprintf("Group %d has %d edges and density %.2f", j , tmp_con, tmp_den))
}
```

Compute the ratio of inner clusters connections to outer ones:

```{r}
for (i in 1:length(setka))
{
tmp_graph = induced.subgraph(yahoo_MUSIC, setka$membership == i)
sum_edges = length(E(yahoo_MUSIC))
coming_ed = length(E(tmp_graph))
outgoing_ed = length(E(induced.subgraph(yahoo_MUSIC,!(setka$membership == i))))
summa_vsego = sum_edges - coming_ed - outgoing_ed
print(sprintf("Ratio for cluster # %d = %.3f",i, coming_ed/summa_vsego))
}
```

### 3. Visualization & interpretation

Visulize five of the most dense clusters. Use names of artists as node labels on the graph.

```{r}
avtori_pesen = scan("artists.txt", what = character(), sep = "\n")

avtori_pesen = avtori_pesen[-yahoo_MUSIC.isolated.vertices]

#Опять делаю чистку

V(yahoo_MUSIC)$label = avtori_pesen


top_result = which(setka_dens %in% sort(setka_dens, decreasing = TRUE)[1:5])
for (i in 1:5) 
{
best_vert = which(setka$membership %in% top_result[i])
top_graph = induced.subgraph(yahoo_MUSIC, best_vert)
plot(top_graph, layout=layout.circle, main=sprintf("Top dense cluster number  %d ", i))
}
```